Parallel air palletization and tour planning for simultaneous pickup and delivery

### 2023-03-29 latex/comp_or.tex
Comp OR paper update

		\State $ts \gets 1.2$ \Comment{torque surplus} \label{mpShims:ts}

@@

Line \ref{mpShims:ts} defines the torque surplus ($ts$). For the $Greedy$ phase, the solution may generate temporary torque unfeasible solutions. We raised the Hypothesis (2) that, in sequential mode, where one pallet is built at a time, torque constraints may be more restrictive than volume or weight constraints, which could stop the palletization process earlier, fostering a solution that may be not as good as it could be. So, we decided to extend torque limit and balance cargo before the next {\it Shims} phase to allow more room for pallet fulfillment.

@@

Line \ref{mpShims:minCGdev} calls the $minCGdev()$ integer programming method (Subsection \ref{subsection:second_phase}) which updates the $nodeTorque$ and $G$. $minCGdev()$ minimizes the CG deviation, bringing it back to its operational range. A proper value for $ts$ must be empirically found to guarantee this intent (the {\it iRace} tool (\cite{LopezIbanezManuel2016}) is good for this value determination).

@@

For each $method$, $scenario$ and $surplus$, 7 different instances were generated. Therefore, 126 tests (6 scenarios $\times$ 3 volumes $\times$ 7 instances) were performed for each method.

The average tour values were presented for $f$ and, for the run time, the worst result obtained. To facilitate the comparison between the methods, we added a last column in these tables, where two values are indicated:
\begin{itemize}
	\item {\bf Normalized}: value between 0 and 1, which corresponds to the ratio between the sum of $f$\/ values obtained by the method in all scenarios and the sum of the best values obtained among all methods in all scenarios. The higher the value of {\bf Normalized}, the closer the method approached the best solutions found.
	\item {\bf Speedup}: ratio of the sums of the worst run times of all scenarios and the sum of the method run times in all scenarios. The method with the highest {\bf Speed-up}\/ is the fastest.
\end{itemize}

In each $scenario$, we indicate in bold the best value of $f$\/ found. In each table, we also indicate in bold the best {\bf Normalized}\/ and {\bf Speed-up}\/ values.

@@

(3) The procedure for 3-D packing generated an unfit item rate of, on average, 17\% after {\it Shims} solutions, 13\% after {\it mpShims} solutions, and 9\% after the MIP solver solutions. 
We are conscious that this unfit rate could be smaller if we had chosen \cite{PaquayLimbourgSchynsOliveira2018} approach, but as we are concerned with an operational application where the running time is crucial, we stick to faster approximate approaches like the {\it First Fit Decreasing} (first orientation that fits) and the {\it Best Fit} (best pivot point if more than one is available).

@@

This solution phase was a multiprocessing 3-D packing with each pallet as a process, which decreased this phase's run time by approximate a $n-1$ factor where $n$ is the number of processes. This was possible because each packing process is completely independent; there is no multiprocessing shared memory. It is also important to highlight that, after the items were excluded, the CG deviation was kept within its operational and feasible range.

@@

@@

Other important contributions are that we verified four hypotheses: Computer parallelism improved {\it Shims} performance; the intermediate integer programming procedure added to {\it Shims} algorithm enhanced it's results; a procedure for 3-D packing was turned possible for operational use due to a process-based parallel computing heuristic, and the integer programming procedure to minimize pallets' travel in the cargo bay was successful.

>>>>

		\State $ts \gets 1.7$ \Comment{torque surplus} \label{mpShims:ts}

@@

Line \ref{mpShims:ts} defines the torque surplus ($ts$). For the $Greedy$ phase, the solution may generate temporary torque unfeasible solutions. We raised the Hypothesis (2) that, in sequential mode, where one pallet is built at a time, torque constraints may be more restrictive than volume or weight constraints, which could stop the palletization process earlier, fostering a solution that may be not as good as it could be. So, we decided to extend torque limit and balance cargo before the next {\it Shims} phase to allow more room for pallet fulfillment. The value $1.7$ was determined by the {\it iRace} tool developed by \cite{LopezIbanezManuel2016}.

@@

Line \ref{mpShims:minCGdev} calls the $minCGdev()$ integer programming method (Subsection \ref{subsection:second_phase}) which updates the $nodeTorque$ and $G$. $minCGdev()$ minimizes the CG deviation, bringing it back to its operational range.

@@

The average tour values were presented for $f$ and, for the run time, the worst result obtained. To facilitate the comparison between the methods, we added a last column in these tables, where two values are indicated:
\begin{itemize}
	\item {\bf Normalized}: value between 0 and 1, which corresponds to the ratio between the sum of $f$\/ values obtained by the method in all scenarios and the sum of the best values obtained among all methods in all scenarios. The higher the value of {\bf Normalized}, the closer the method approached the best solutions found.
	\item {\bf Speedup}: ratio of the sums of the worst run times of all scenarios and the sum of the method run times in all scenarios. The method with the highest {\bf Speedup}\/ is the fastest.
\end{itemize}

In each $scenario$, we indicate in bold the best value of $f$\/ found. In each table, we also indicate in bold the best {\bf Normalized}\/ and {\bf Speedup}\/ values.

@@

(3) The procedure for 3D packing generated an unfit item rate of, on average, 17\% after {\it Shims} solutions, 13\% after {\it mpShims} solutions, and 9\% after the MIP solver solutions. 
We are conscious that this unfit rate could be smaller if we had chosen \cite{PaquayLimbourgSchynsOliveira2018} approach, but as we are concerned with an operational application where the running time is crucial, we stick to faster approximate approaches like the {\it First Fit Decreasing} (first orientation that fits) and the {\it Best Fit} (best pivot point if more than one is available).

@@

This solution phase was a multiprocessing 3D packing with each pallet as a process, which decreased this phase's run time by approximate a $n-1$ factor where $n$ is the number of processes. This was possible because each packing process is completely independent; there is no multiprocessing shared memory. It is also important to highlight that, after the items were excluded, the CG deviation was kept within its operational and feasible range.

It is important to  emphasize that, as the {\it Multiprocessing 3D packing} is a post-optimization procedure, it benefited all three resolution methods.

@@

Another important fact is the inversion of quality results between {\it Shims} and {\it mpShims}. In Table \ref{tab:results}, {\it Shims} was better, but, in Table \ref{tab:results2} (with the inclusion of the {\it Multiprocessing 3D packing}), {\it mpShims} surpassed {\it Shims}' results. The rationale behind this is that .....

@@

Other important contributions are that we verified four hypotheses: Computer parallelism improved {\it Shims} performance; the intermediate integer programming procedure added to {\it Shims} algorithm enhanced it's results; a procedure for 3D packing was turned possible for operational use due to a process-based parallel computing heuristic, and the integer programming procedure to minimize pallets' travel in the cargo bay was successful.
